\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{setspace}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formattingZ
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeItemsss}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-0.8pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItemsss{#1}{#2}\vspace{-1pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/zhiaozhou/}{\Large Zhiao Zhou}} & Email : \href{mailto:zz1749@nyu.edu}{zz1749@nyu.edu}\\
  \href{http://zhiaozhou.top/}{http://zhiaozhou.top/} & Mobile : 18917630007 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Online (Conferred with On-campus Degree)}
      {Master of Science in Computer Science with a Machine Learning track}{Aug. 2018 -- Jun. 2022}
    \resumeSubheading
      {New York University}{New York, USA}
      {Master of Science in Urban Data Science \hspace{0.55cm} GPA: 3.57}{Aug. 2017 -- Aug. 2018}
      
      {- Major courses: Applied Data Science, Machine Learning, Deep Learning, Urban Spatial Analysis, Real Time and Big Data Analytics}
    \resumeSubheading
      {Shanghai University of Finance \& Economics}{Shanghai, China}
      {Bachelor of Economics in Actuarial Science}{Sept. 2013 -- Jun. 2017}
      
      {- Major courses: Accounting, Macro \& Microeconomics, Corporate Finance, Investments, Financial Modeling, Stochastic Process, Surviving Model}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {New York University}{New York, USA}
      {Research Assistant}{Mar. 2018 - Aug. 2018}
      \resumeItemListStart
        \resumeItem{Wrote a Twitter Crawler to obtain all the tweets during the Hurricane Harvey.}{}
        \resumeItem{Trained an LSTM with embedding matrix to detect fake news and rumors during hurricane Harvey in Houston.}{}
      \resumeItemListEnd

    \resumeSubheading
      {Guotai Junan Securities}{Shanghai, China}
      {Quant Intern, Department of e-Finance}{Dec. 2017 - Jan. 2018}
      \resumeItemListStart
        \resumeItem{Develop quantitative security selection strategies for retail investors in China based on research papers}{}
        \resumeItem{Developed 4 Event-Driven Strategies and 1 ROE Value Investing Strategy.}{}
        \resumeItem{Accomplish the quantitative demands raised by other teams.}{}
      \resumeItemListEnd

    \resumeSubheading
      {Orient Securities}{Shanghai, China}
      {Researcher Assistant Intern, Tactic Team, Equity Research Department}{Feb. 2017 - May. 2017}
      \resumeItemListStart
        \resumeItem{Developed the daily equity strategy report template including key indicators tracking, stock market replay, comments on important news and trend analysis.}{}
        \resumeItem{Written over 30 daily reports with at least 200 views per day, 628 at max.}{}
        \resumeItem{Assisted researcher on several in-depth equity strategies reports including Nifty 50, the Belt and Road, A large bay area of Guangdong, etc.}{}
      \resumeItemListEnd
      
    \resumeSubheading
      {Haitong Securities}{Shanghai, China}
      {Researcher Assistant Intern, Equity Research Department}{Dec. 2016 - Feb. 2017}
      \resumeItemListStart
        \resumeItem{Daily nonferrous metal industrial research report (Public).}{}
        \resumeItem{Worked on several corporation research report with profit forecast.}{}
        \resumeItem{Collecting data regarding the industry and corporations using Wind.}{}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Traffic Density Detector}
      {A Faster RCNN with Inception ResNet V2 object detection model for measuring traffic density under any traffic cams}
    \resumeSubItem{Overlapping Digits Segmentation}
      {A CapsNet model for segmenting two highly overlapping digits which outperforms a CNN model.}
    \resumeSubItem{Chinese Stock Prediction Using Weibo \& Baidu News Sentiment}
      {A neural network regression model to predict the mean stock price percentage change everyday using financial factors along with corresponding Sina Weibo and Baidu News sentiment scores.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, R, HTML, CSS, JavaScript}
     \hfill
     \textbf{Technologies}{: Tensorflow, Keras, Hive, HBase, Spark}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
